Grounding the interaction: anchoring situated discourse in everyday human-robot interaction

### 2011-07-17 paper_knowledge.tex
Raquel: Fixed typos/grammar
(Raquel, I prefer to keep with UK spelling when possible, thus 'behaviour' and not 'behavior' for instance)

This list does not cover all the possible features that could be exposed by a
symbolic knowledge management system. Bio-inspired memory management (the
ability to forget or reinforce knowledge) or curiosity (the ability to identify
lacking knowledge and actively trigger behaviours to acquire it -- Hawes et
al.~\cite{Hawes2011} have contributions in this field, with their \emph{Dora}
robot which is endowed with motivation mechanisms to explore unknown parts of
the environment), to give some examples, could arguably be added to the list.
However, this first analysis sets a convenient reference frame to understand
and evaluate knowledge representation systems, including the \textsc{ORO}
knowledge management system we propose.

@@

Knowledge is represented in ORO in the Description Logics formalism (using the
OWL-DL -- \emph{Web Ontology Language - Description Logics} -- language), as
RDF (\emph{Resource Description Framework}) triples (for instance \stmt{robot
isIn kitchen}). We use the Jena\footnote{\url{http://jena.sourceforge.net/}}
framework as the underlying library to load and build in-memory OWL model. We
use it in conjunction with the
Pellet\footnote{\url{http://clarkparsia.com/pellet/}} reasoner to ensure the
continuous classification of the OWL concept graph: at run-time, newly added
statements are continuously reasoned about (\emph{classified}), and at any time,
the server expose a complete set of statements, both the asserted ones and the
inferred ones. For instance, if \stmt{socrates type Human} and \stmt{Human
subClassOf Mortal} are asserted, the server transparently adds the inferred
statement \stmt{socrates type Mortal}, and a later query retrieving all mortal
entities would return \concept{socrates} as well. The language of the OWL
family use the \emph{Open World Assumption} (if a fact can not be inferred as
true, it does not mean that it is inferred to be false), and the Pellet
reasoner honors this assumption as well.

@@

\item \emph{Points At}: verifies whether an object is pointed at by an agent. This
relation is particularly useful during interaction when one of the agents is
referring to an object saying ``this" or ``that" while pointing at it.

@@

\item \emph{Reachable}: it allows the robot to estimate the agent's capability
to reach an object, which is fundamental for task planning. For example, if the
user asks the robot to give her an object, the robot must compute a transfer
point where the user is able to get the object afterward.

@@

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier2001} presented different models to define the
\emph{above} relation; \cite{Kelleher2009} presented two computational models of topological and projective spatial prepositions; \cite{Blisard2005} employed contour points of segmented objects to determine \emph{front, behind, left,right} relations). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):

@@

In order to better understand the overall process the {\sc Dialogs} module and its relation with ORO, we next describe the different steps of the approach based on three examples. In these examples, we
assume that some initial facts are present in the knowledge base, both in the
robot's own model and in the human's model.  Since the robot tries to ground a
human utterance, all queries are sent to the human model in order to interpret
it from the human perspective.

>>>>

This list does not cover all the possible features that could be exposed by a
symbolic knowledge management system. Bio-inspired memory management (the
ability to forget or reinforce knowledge) or curiosity (the ability to identify
lacking knowledge and actively trigger behaviours to acquire it --Hawes et
al.~\cite{Hawes2011} have contributed in this area with \emph{Dora}, a
robot endowed with motivation mechanisms to explore unknown regions of
the environment--), to give some examples, could arguably be added to the list.
However, this first analysis sets a convenient reference frame to understand
and evaluate knowledge representation systems, including the \textsc{ORO}
knowledge management system we propose.

@@

Knowledge is represented in ORO in the Description Logics formalism (using the
OWL-DL --\emph{Web Ontology Language - Description Logics}-- language), as
RDF (\emph{Resource Description Framework}) triples (for instance \stmt{robot
isIn kitchen}). We use the Jena\footnote{\url{http://jena.sourceforge.net/}}
framework as the underlying library to load and build in-memory OWL model. We
use it in conjunction with the
Pellet\footnote{\url{http://clarkparsia.com/pellet/}} reasoner to ensure the
continuous classification of the OWL concept graph: at run-time, newly added
statements are continuously reasoned about (\emph{classified}), and at any time,
the server exposes a complete set of statements, both the asserted ones and the
inferred ones. For instance, if \stmt{socrates type Human} and \stmt{Human
subClassOf Mortal} are asserted, the server transparently adds the inferred
statement \stmt{socrates type Mortal}, and a later query retrieving all mortal
entities would return \concept{socrates} as well. The language of the OWL
family use the \emph{Open World Assumption} (if a fact can not be inferred as
true, it does not mean that it is inferred to be false), and the Pellet
reasoner honors this assumption as well.

@@

\item \emph{Points At}: verifies whether an object is pointed at by an agent. This
relation is particularly useful during interaction when one of the agents is
referring to an object saying ``this" or ``that" while pointing at it. Section~\ref{disamb-gestures} describes in more detail the combination of both sources of information (verbal and non-verbal).

@@

\item \emph{Reachable}: it allows the robot to estimate the agent's capability
to reach an object, which is fundamental for task planning. For example, if the
user asks the robot to give him/her an object, the robot must compute a transfer
point where the user is able to get the object afterward.

@@

\item \emph{Location according to an object}: We can also refer to object
locations with respect to other objects in the environment, such as \emph{above,
next to, in}, etc. These types of relations are widely studied in language
grounding (\eg \cite{Regier2001} presented different models to define the
\emph{above} relation; \cite{Kelleher2009} introduced two computational models of topological and projective spatial prepositions; \cite{Blisard2005} employed contour points of segmented objects to determine \emph{front, behind, left,right} relations). In this work we use similar models based on the
bounding boxes and center of mass of the objects to define three main relations
(Figure~\ref{fig::sprelation}):

@@

In order to better understand the overall process of the {\sc Dialogs} module and its relation with ORO, we next describe the different steps of the approach based on three examples. In these examples, we
assume that some initial facts are present in the knowledge base, both in the
robot's own model and in the human's model.  Since the robot tries to ground a
human utterance, all queries are sent to the human model in order to interpret
it from the human perspective.
